---
title: "Goal Programming"
output:
  pdf_document: default
  html_notebook:
    highlight: textmate
    theme: cerulean
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


This document contains the code for Goal Programming for the R&D Division of Emax Corp

# R&D Division of Emax Co.

```{r}
library(lpSolveAPI)
gp <- read.lp("rnd.lp")
gp
```
## Solve
```{r}
solve(gp)
get.objective(gp)
get.variables(gp)
```

### Remarks

Applying the simplex method to this formulation yields an optimal solution of x1 = 0, x2 = 0, x3 = 15, y1p = 25, y1m = 0, y2m = 0, y2p = 0. Note that the solution is given in the order in which the variables appear in the formulation. This implies that y2 = 0, so the next year earnings goal is fully satisfied, but the employment goal is exceeded by 25 (2500 employees). which will reduce the profit by 150 (6*25). As a result of that, Z is equal to 225. 








